Automatic Matching of Bullet Lands

### 2016-01-16 imaging-paper.Rnw
Lands from known bullets

\section{Evaluation}
In order to get a better understanding of  how  the matching algorithm works in known matches and non-matches, we investigate its performance in a test scenario based on the James Hamby study.
As a first step, we automatically assess the quality of each of the lands by  checking that we can identify a stable region on each land. For this, we compute the cross-correlation of signatures at cross sections 25$\mu m$ apart. For a stable region, we require a minimum of 0.9 for the cross correlation. Four lands from different bullets are flagged as problematic in this respect. A visual inspection (see Figure~\ref{fig:fourflags}) shows that each one of these lands has scratch marks across the surface, also known as `tank rash'.
%
\begin{figure}
  \centering
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 6 Bullet 2-1}
%' <<echo=FALSE>>=
%' b1 <- read.x3p(file.path(datadir, "Br6 Bullet 2-1.x3p"))
%' image(b1$surface.matrix)
%' @
\includegraphics[width=\textwidth]{images/br6-2-1-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 9 Bullet 2-4}
\includegraphics[width=\textwidth]{images/br9-2-4-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet B-2}
\includegraphics[width=\textwidth]{images/b-2-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet Q-4}
\includegraphics[width=\textwidth]{images/q-4-grey.png}
\end{subfigure}
\caption{\label{fig:fourflags}Images of the four lands that got flagged during the quality assessment. All of them show scratch marks (tank rash) across the striation marks from the barrel. They are excluded from the remainder of the analysis.}
\end{figure}
%
We exclude these four lands from further matching considerations and 
 run all remaining lands from the unknown bullets against all remaining lands from known bullets for matches, i.e. we are running $15 \times 6 -2 = 90 - 2 = 88$ lands from unknown bullets against $2 \times 10 \times 6 -2 = 120 - 2 = 118$ lands from known bullets, yielding a total of $10,384$ land-to-land comparisons. Out of these comparisons, there are 172 known matches (KM), while the rest are known non-matches (KNM). 
 When things go perfectly, they look like the results in Figure~\ref{fig:hamby-perfect}: Figure~\ref{fig:hamby-perfect}a shows the distribution of the number of maximum consecutive matching striae between land C-3 and all 118 known lands. Two lands show a high CMS. These correspond to the known matches with C-3, shown in Figures~\ref{fig:hamby-perfect}b and~\ref{fig:hamby-perfect}c. 
 Unfortunately, not all results are as clear cut. 
It might not be reasonable to assume that we can match all lands, but the idea is to try to maximize the number of matches to get an overview of what we might be able to expect from an automated match.

>>>>

\section{Evaluation}
In order to get a better understanding of  how  the matching algorithm works in known matches and non-matches, we investigate its performance in a test scenario based on the James Hamby study.
As a first step, we automatically assess the quality of each of the lands by  checking that we can identify a stable region on each land. For this, we compute the cross-correlation of signatures at cross sections 25$\mu m$ apart. For a stable region, we require a minimum of 0.9 for the cross correlation. Four lands from different bullets are flagged as problematic in this respect. A visual inspection (see Figure~\ref{fig:fourflags}) shows that each one of these lands has scratch marks across the surface, also known as `tank rash'.
%
\begin{figure}
  \centering
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 6 Bullet 2-1}
%' <<echo=FALSE>>=
%' b1 <- read.x3p(file.path(datadir, "Br6 Bullet 2-1.x3p"))
%' image(b1$surface.matrix)
%' @
\includegraphics[width=\textwidth]{images/br6-2-1-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Barrel 9 Bullet 2-4}
\includegraphics[width=\textwidth]{images/br9-2-4-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet B-2}
\includegraphics[width=\textwidth]{images/b-2-grey.png}
\end{subfigure}
\begin{subfigure}[t]{.49\textwidth}\centering
\caption{Unknown Bullet Q-4}
\includegraphics[width=\textwidth]{images/q-4-grey.png}
\end{subfigure}
\caption{\label{fig:fourflags}Images of the four lands that got flagged during the quality assessment. All of them show scratch marks (tank rash) across the striation marks from the barrel. They are excluded from the remainder of the analysis.}
\end{figure}
%
We exclude these four lands from further matching considerations and 
 run all remaining lands from the unknown bullets against all remaining lands from known bullets for matches, i.e. we are running $15 \times 6 -2 = 90 - 2 = 88$ lands from unknown bullets against $2 \times 10 \times 6 -2 = 120 - 2 = 118$ lands from known bullets, yielding a total of $10,384$ land-to-land comparisons. Out of these comparisons, there are 172 known matches (KM), while the rest are known non-matches (KNM). 
 When things go perfectly, they look like the results in Figure~\ref{fig:hamby-perfect}: Figure~\ref{fig:hamby-perfect}a shows the distribution of the number of maximum consecutive matching striae between land C-3 and all 118 lands from known bullets. Two lands show a high CMS. These correspond to the known matches with C-3, shown in Figures~\ref{fig:hamby-perfect}b and~\ref{fig:hamby-perfect}c. 
 Unfortunately, not all results are as clear cut. 
It might not be reasonable to assume that we can match all lands, but the idea is to try to maximize the number of matches to get an overview of what we might be able to expect from an automated match.
